### 2019-01-25 journal/experiments.tex
change operator text

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.  More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC, it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, two additional faults are revealed in the first 50 examined tests.

>>>>

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.  More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC, it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, two additional faults are revealed in the first 50 examined tests.  Operator selection can, in principle (and in one case in our data set, in practice) reduce the effectiveness of fault localization.  However, with hot mutants, it is easy, if localization using only negations and deletions is not helpful, to use the same method as proposed above for random selection to compute a more precise localization for a test.  This should usually not be required, however:  we noted that in most cases where a mutant involved in a localization did use a operator replacement, the mutant was usually equivalent in behavior to a condition negation.  Constant replacement repairs were simply very rare and not involved in any of the useful compiler localizations.  The problem observed with random sampling, that the metric of distances to other tests may be inaccurate, is less of concern with operator selection:  as far as we can tell, based on FPF discovery curves and APFD, distances are \emph{more} accurate using only the mutants we propose.
